---
title: "Figure4"
author: "Leslie Roberson"
date: "28/01/2022"
output: html_document
---

## Summary

As per the Deed of Confidentiality with AFMA, we are not permitted to provide the data showing summary statistics for individual vessels.

For the sake of transparency, we show the code used to make the figure, although it is not reproducible without the data.

Note that final formatting (fonts, bycatch species icons) was done in Adobe Illustrator.

```{r setup, include=FALSE}

library(tidyverse)
library(here)

knitr::opts_chunk$set(echo = TRUE)
```

Bycatch ratio divided by max of that fishery/species 
But with one panel for each species (colors for fisheries)

```{r fig4 plot}

names(fig4.dat) # not publicly available

pal_fishery <- lisa_palette("MarcChagall", 5, "discrete")

fig4 <- fig4.dat %>% 
    group_by(Fishery_lab, shot_id, bycatch_type_label) %>%
    # adjust zeros for log scale
    mutate(target_catch=ifelse(target_catch==0, 0.1, target_catch),
           byc_ratio = bycatch_cnt/target_catch) %>%
    ungroup() %>%
    group_by(fshry_spp, Year, vessel, Fishery_lab) %>%
    summarise(avg_ratio=mean(byc_ratio)) %>%
    ungroup() %>%
    group_by(fshry_spp, Fishery_lab) %>%
    mutate(avg_max=max(avg_ratio)) %>%
    #distinct(Fishery_lab, bycatch_type_label, avg_max)
    ggplot(aes(x=Year, y=avg_ratio/avg_max, color=Fishery_lab)) +
    geom_point(aes(x=Year, y=avg_ratio/avg_max, color=Fishery_lab)) + 
    scale_color_manual(values = pal_fishery) +
  scale_y_continuous(expand=expand_scale(0,0.1)) +
  scale_x_continuous(limits=c(2001,2021), breaks=c(2004, 2012, 2020)) +
    facet_wrap(~fshry_spp, 
               labeller = as_labeller(c('Tuna longlines Seabirds'="Seabirds", `Tuna longlines Sea turtles`="Sea turtles", `Tuna longlines Shortfin mako`="Shortfin mako", `Prawn trawl Syngnathids`="Syngnathids", `Prawn trawl Hammerhead sharks`="Hammerhead sharks", `Prawn trawl Sea snakes`="Sea snakes", `Prawn trawl Sawfishes`="Sawfishes", `Otter bottom trawl Seabirds`="Seabirds", `Otter bottom trawl Pinnipeds`="Pinnipeds", `Demersal longlines Seabirds`="Seabirds", `Demersal longlines Gulper sharks`="Gulper sharks", `Demersal longlines School shark`="School shark", `Set gillnets Seabirds`="Seabirds", `Set gillnets Hammerhead sharks`="Hammerhead sharks", `Set gillnets Dolphins`="Dolphins"))) + 
    #scale_y_continuous(trans="pseudo_log",  breaks=pretty_breaks(n=6)) + 
    labs(x = "Year", y = "Relative ratio of interactions to target catch") +
    theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        legend.title= element_blank(),
        legend.position=c(0.88, 0.08), # inside the missing facet
        legend.text = element_text(size = 8.5),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-5,-5,-5,-5),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.spacing.y = unit(-0.5, 'cm'),
        #legend.text = element_text(margin = margin(r = 2, unit = "pt")),
        strip.background =element_rect(fill="NA", color ="black"), # facet label boxes fill white instead of gray
        panel.border = element_rect(fill = NA, color = "black"), # keep facet label borders
        legend.key = element_rect(fill = NA)) 
    #guides(color = guide_legend(byrow=TRUE, nrow=1, override.aes = list(size = 3)))
fig4

```

